---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
setwd("C:/Users/dtek_2/Documents/GitHub/RepData_PeerAssessment1")
library(XML)
narcissus <- read.csv(file = "activity.csv", header = TRUE)
head(narcissus)
summary(narcissus)

```

## What is mean total number of steps taken per day?

We can find the median and mean total number of steps by aggregating
the steps by date and then taking the mean.

Note:  8 days (e.g. 1 Oct 2012) have only NAs, and so when calculating the
mean, they will just be ignored.

```{r}

tot_steps <- aggregate(narcissus$steps, by=list(narcissus$date), FUN=sum)
colnames(tot_steps) <- c("date", "steps")
mean_steps <- mean(tot_steps$steps, na.rm = TRUE)
mean_steps
median_steps <- median(tot_steps$steps, na.rm = TRUE)
median_steps
hist(tot_steps$steps, breaks=8)
```



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
